---
title: "2: Lab SetUp IMPORTANT"
output: html_document
runtime: shiny
---


```{r setup, include=FALSE}
# OPTIONS -----------------------------------------------
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message = FALSE)
```

```{r, include=FALSE}

# PACKAGES-----------------------------------------------
# Tutorial packages
library(vembedr)
library(skimr)
library(yarrr)
library(RColorBrewer)
library(GGally) 
library(tidyverse)
library(plotly)
library(readxl)
library(rvest)
library(biscale)
library(tidycensus)
library(cowplot)
library(units)
library(shiny)
library(data.table)

# FUNCTIONS -----------------------------------------------
# Get R version
GetRLatest <- function(Website="https://cran.r-project.org/banner.shtml"){
   require(rvest)
   
   #scrape the text from the website
   RWebsite <- read_html("https://cran.r-project.org/banner.shtml") %>%
            html_nodes("li") %>%
            html_text()
   
   # get the line that includes latest release and get rid of the stuff after
   RLatest <- base::strsplit(RWebsite[grep("latest release",
                                     tolower(RWebsite))],"\n")[[1]][1]
   return(RLatest)
}

```

# Overview

There are a number of software and internet accounts you will need. This tutorial takes you through them. DO NOT SKIP

<br>

#### ["I already have R and R studio on my laptop"]{.underline}

-   IT IS VERY IMPORTANT THAT EVERYONE IS RUNNING THE MOST UP-TO-DATE VERSION OF R AND RStudio. <br>

-   The easiest way to update is to re install. You will not lose access to old work. Follow these instructions verbatim.

<br><br>


# Test your knowledge

Try this quiz!

<br>

```{r, echo=FALSE}
# Source the Shiny app script
source("app.R")

# Run the Shiny app
shinyApp(ui = ui, server = server)
```